\documentclass[12pt,a4paper,sans]{moderncv}	% possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\moderncvstyle{suchyta}                         % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking' 
\moderncvcolor{black}                           % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black' 

%\renewcommand{\familydefault}{\sfdefault}      % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page


\usepackage[top=0.75in, bottom=0.75in, left=0.75in, right=0.75in]{geometry}
\usepackage{tabularx,textcmds,amsmath,amsfonts}


% personal data
\name{Eric}{Suchyta}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

% Commands for myself
%\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{1ex}

\newcommand{\suchytatitle}{%
\begin{center}
\namestyle{Eric~Suchyta}\titlestyle{~|~Curriculum Vitae} \\
\end{center}
%
\begin{minipage}[!t]{0.49\textwidth}
	Computer Science and Mathematics Division \\
	Oak Ridge National Laboratory \\
	P.O. Box 2008 \\
	Oak Ridge, TN 37831 \\
\end{minipage}
%
\begin{minipage}[!t]{0.50\textwidth}
email: \href{mailto:eric.d.suchyta@gmail.com}{eric.d.suchyta@gmail.com}\\
%website: {\url{http://www.sas.upenn.edu/~esuchyta}} \\
Office: Building 4100, C234 \\
Phone: (865) 576-6340 \\ \\
\end{minipage}
}


\begin{document}
\suchytatitle{}


\section{Research Interests}
Exascale computing;
I/O efficiency at scale;
Fusion physics simulations;
Astronomical imaging surveys


\newcommand{\tsp}{\\[0.5em]}
\section{Positions Held}
\begin{tabularx}{\linewidth}{l X}
2016 - : & Computer Scientist \\ & Computer Science and Mathematics Division, Oak Ridge National Laboratory \tsp
2015 - 2016: & Postdoctoral Researcher \\ & Department of Physics \& Astronomy, University of Pennsylvania \tsp
2010 - 2015: & Graduate Research Assistant, (Advisor: Klaus Honscheid) \\& Department of Physics, The Ohio State University \tsp
2013 - 2014: & Dark Energy Survey Early Career Scientist Committee Chair \tsp
2010 - 2013: & Graduate Teaching Assistant \\& Department of Physics, The Ohio State University \tsp
2009 - 2010: & Undergraduate Research Associate, (Advisor: Jim Beatty) \\& Department of Physics, The Ohio State University \tsp
2007 - 2009: & Undergraduate Research Associate, (Advisor: R. Sooryakumar) \\& Department of Physics, The Ohio State University \tsp
\end{tabularx}
\section{Education}
\begin{tabularx}{\linewidth}{l X}
2015: & Ph.D., Physics, The Ohio State University \\
2012: & M.S., Physics, The Ohio State University \\
2010: & B.S., Physics, The Ohio State University, With Research and Honors Distinction, Summa Cum Laude, French Literature Minor
\end{tabularx}

\section{Honors and Awards}
\begin{tabularx}{\linewidth}{l X}
2017: & Oak Ridge National Laboratory FY17 distinguished employee \\
2014: & The Ohio State University Presidential Fellowship Award \\
2014: & Dark Energy Survey Builder Status \\
2010: & Smith Senior Award, Department of Physics, The Ohio State University \\
2009: & Smith Junior Award, Department of Physics, The Ohio State University  \\
2009: & The President's Salute to Undergraduate Academic Achievement at The Ohio State University \\
2007: & Helen Cowan Book Award, Department of Physics, The Ohio State University  \\
2006: & The Ohio State University Medalist Scholarship
\end{tabularx}


\section{Miscellaneous}
\begin{achievements}
\item Work highlighted for a general reading audience in \textit{Fermilab Today}
\item Observing experience, Blanco Telescope, DECam, 6 nights
\item Member of the American Physical Society and the Institute of Electrical and Electronics Engineers
\item Contributions to numerous science outreach projects including volunteer teaching/mentoring, blog writing/editing, competition/poster judging
\end{achievements}

\clearpage
%\section{Publications}

%\mypublications


\nociteselected{*}
\bibliographystyleselected{suchyta-bib}
\bibliographyselected{suchyta-papers-selected-modified}
%\bibliographyselected{suchyta-papers-selected-modified}


\section{Presentations}

\begin{achievements}
\item Digging Deeper (and More Greedily) in Imaging Surveys. \textit{Computer Science and Mathematics Division Seminars}, Oak Ridge National Laboratory. 10 Mar. 2016.
\item Digging Deeper (and More Greedily) in Imaging Surveys. \textit{IFAE Pizza Seminars}, Institut de F\'isica d'Altes Energies, Universitat Aut\`onoma de Barcelona. 14 Oct. 2015.
\item A General Prescription for Digging Too Deeply in Imaging Surveys. \textit{American Physical Society April Meeting}, Baltimore, MD. 14 Apr. 2015.
\item Clustering, Proximity, and Balrog. \textit{CCAPP Summer Seminar Series}, Center for Cosmology and Astroparticle Physics, The Ohio State University. 01 Jul. 2014.
\item Can we do lensing with DECam? \textit{American Physical Society Division of Particles and Fields Meeting}, Santa Cruz, CA. 08 Aug. 2013. 
\item How Galaxy Physics Can Help Us Understand Weak Lensing. \textit{American Physical Society Division of Particles and Fields Meeting}, Santa Cruz, CA. 08 Aug. 2013. 
\end{achievements}


\section{Other Documents}
\begin{achievements}
\item Ph.D. Thesis: Embrace the Dark Side: Advancing the Dark Energy Survey. The Ohio State University, 2015.
\item Accepted Proposal: Precise mass profiles of CLASH galaxy clusters through spectroscopy of HST-selected lensed objects, LBT 2014A.
\item Senior Honors Thesis: Signal Stability Studies with the Askaryan Under-Ice Radio Array. The Ohio State University, 2010.
\end{achievements}


\nociteadditional{*}
\bibliographystyleadditional{suchyta-bib}
%\bibliographyadditional{suchyta-papers-additional-modified}
\bibliographyadditional{suchyta-papers-FY18-modified}


\section{References}
\begin{minipage}{0.48\textwidth}
\textbf{Klaus Honscheid} \\
Department of Physics \\
The Ohio State University \\
191 West Woodruff Avenue \\
Columbus OH, 43210 USA \\
+1 (614) 292-3287 \\
kh@mps.ohio-state.edu \\
\\
\textbf{Gary Bernstein} \\
Department of Physics \& Astronomy \\
University of Pennsylvania \\
209 South 33rd Street \\
Philadelphia, PA 19104 USA \\ 
+1 (215) 573-6252 \\
garyb@physics.upenn.edu
\end{minipage}%
%
\begin{minipage}{0.48\textwidth}
\textbf{Eric Huff} \\
Department of Physics \\
The Ohio State University \\
191 West Woodruff Avenue \\
Columbus OH, 43210 USA \\
+1 (614) 292-7369 \\
huff.791@osu.edu \\
\\
\textbf{Jelena Aleksi\'c} \\
Institut de F\'isica d'Altes Energies \\
Universitat Aut\`onoma de Barcelona \\
E-08193 Bellaterra, Barcelona, Spain \\
+34 93 176 3966 \\
jelena@ifae.es \\
\end{minipage}


%\textbf{Brian Yanny} \\
%Computing Sector \\
%Fermi National Accelerator Laboratory \\
%P.O. Box 500 \\
%Batavia, IL 60510 USA \\
%+1 (630) 840-4413 \\
%yanny@fnal.gov \\
%\end{minipage}

%\textbf{Josh Frieman} \\
%Department of Astronomy and Astrophysics \\
%The University of Chicago \\
%5640 S. Ellis Ave. \\
%Chicago, IL 60637 USA \\ 
%+1 (773) 702-7971 \\
%frieman@fnal.gov \\
%\end{minipage}%

%\begin{minipage}{0.48\textwidth}
%\textbf{Sarah Bridle} \\
%The University of Manchester \\
%School of Physics and Astronomy \\
%Oxford Road \\
%Manchester, M13 9PL, UK \\
%+44 (0) 161 275 4042 \\
%sarah.bridle@manchester.ac.uk \\
%\\


%\nocite{*}
%\bibliographystyle{mn2e_adsurl}

%\bibliography{suchyta-publications}                        % 'publications' is the name of a BibTeX file

\end{document}


